---
title: "Homework Four Submission 1"
author: "Safia Read"
format:
  pdf:
    output-file: "read-s-hwk4-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

This is my first submission of the fourth homework for Econ 470. 

[Link to Github](https://github.com/safiaread/homework_4)

https://github.com/safiaread/homework_4

```{r, echo = F, message = F}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, fixest, xtable, modelsummary)
data <- read_rds("/Users/safiaread/Desktop/homework_4/data/output/final_ma_data.rds")
data <- data %>% 
subset(year >= 2010 & year <= 2015 & snp == "No" & premium_partc == 0 & (planid < 800 | planid >= 900))
```

Question 1
It looks like the number of plans is pretty low.
```{r, echo = F}
data %>%
  group_by(county) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = "", y = count)) +
  geom_boxplot() +
  labs(title = "Boxplot of Counts by County", x = "County", y = "Count")
```

Question 2
The star ratings have increased generally. 
```{r, echo = F}
data%>%
filter(year == 2010)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()

data%>%
filter(year == 2012)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()

data%>%
filter(year == 2015)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()
```

Question 3

The average benchmark has fallen according to this graph, but I think the variable calculation is off.
```{r, echo = F}
q3 <- data%>%
group_by(year)%>%
summarise(avg_benchmark = mean(payment_partc, na.rm = T))

ggplot(q3, aes(x = year, y = avg_benchmark))+
geom_line()
```

Question 4

Medicare Advantage has increased in popularity over time. I would expect that to correlate with increased benchmark payments.
```{r, echo = F}
q4 <- data %>%
  group_by(year) %>%
  summarize(med_prop = sum(avg_enrollment, na.rm = TRUE) / sum(avg_eligibles, na.rm = TRUE))
  
ggplot(q4, aes(x = year, y = med_prop)) +
geom_line()
```

Question 5
```{r, echo = F}
data_raw <- data %>%
  mutate(raw_rating=rowMeans(
    cbind(breastcancer_screen,rectalcancer_screen,cv_cholscreen,diabetes_cholscreen,
          glaucoma_test,monitoring,flu_vaccine,pn_vaccine,physical_health,
          mental_health,osteo_test,physical_monitor,primaryaccess,
          hospital_followup,depression_followup,nodelays,carequickly,
          overallrating_care,overallrating_plan,calltime,
          doctor_communicate,customer_service,osteo_manage,
          diabetes_eye,diabetes_kidney,diabetes_bloodsugar,
          diabetes_chol,antidepressant,bloodpressure,ra_manage,
          copd_test,betablocker,bladder,falling,appeals_timely,
          appeals_review),
    na.rm=T)) %>%
  select(contractid, planid, fips, avg_enrollment, state, county, raw_rating, partc_score,
         avg_eligibles, avg_enrolled, premium_partc, risk_ab, Star_Rating,
         bid, avg_ffscost, ma_rate)

q5 <- data_raw %>%
  select(raw_rating) %>%
  mutate(three = sum(ifelse(raw_rating >= 2.75 & raw_rating < 3.25, 1, 0), na.rm = T), three_five = sum(ifelse(raw_rating >= 3.25 & raw_rating < 3.75, 1, 0), na.rm = T), four = sum(ifelse(raw_rating >= 3.75 & raw_rating < 4.25, 1, 0), na.rm = T), four_five = sum(ifelse(raw_rating >= 4.25 & raw_rating < 4.75, 1, 0), na.rm = T), five = sum(ifelse(raw_rating <= 3.75, 1, 0), na.rm = T))%>%
  head(n=1)


q5
```

Question 6
```{r, echo = F}
data.rd1 <- data_raw %>%
  filter(Star_Rating==2.5 | Star_Rating==3)%>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window1 = (score>=-.125 & score<=.125),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star25.1 <- lm(mkt_share ~ score + treat, data=data.rd1)
star25.2 <- lm(mkt_share ~ score + treat, data= (data.rd1 %>% filter(window1==TRUE)))
star25.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd1 %>% filter(window1==TRUE)))
est1 <- as.numeric(star25.1$coef[3])
est2 <- as.numeric(star25.2$coef[3])
est3 <- as.numeric(star25.3$coef[3])

bandwidth <- c("0.2", "0.125", "0.125")
estimates <- c(est1, est2, est3)

three_stars <- data.frame(bandwidth,estimates)
three_stars

#rows <- tribble(~term, ~ m1, ~ m2, ~ m3 ,
              #  'Bandwidth', "0.25", "0.125", "0.#125")
#attr(rows, 'position')  <- 7

#modelsummary(list(star25.1, star25.2, star25.3),
         # keep=c("score", "treatTRUE", "score_treat"),
         # coef_map=c("score"="Raw Score", 
        #            "treatTRUE"="Treatment",
         #           "score_treat"="Score x Treat"),
        #  gof_map=c("nobs", "r.squared"),
        #  add_rows=rows)

data.rd2 <- data_raw %>%
  filter(Star_Rating==3 | Star_Rating==3.5) %>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window1 = (score>=-.125 & score<=.125),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star35.1 <- lm(mkt_share ~ score + treat, data=data.rd2)
star35.2 <- lm(mkt_share ~ score + treat, data= (data.rd2 %>% filter(window1==TRUE)))
star35.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd2 %>% filter(window1==TRUE)))
est1 <- as.numeric(star35.1$coef[3])
est2 <- as.numeric(star35.2$coef[3])
est3 <- as.numeric(star35.3$coef[3])

bandwidth <- c("0.2", "0.125", "0.125")
estimates <- c(est1, est2, est3)

threefive_stars <- data.frame(bandwidth,estimates)
threefive_stars

#rows <- tribble(~term, ~ m1, ~ m2, ~ m3 ,
              #  'Bandwidth', "0.25", "0.125", "0.125")
#attr(rows, 'position')  <- 7

#modelsummary(list(star35.1, star35.2, star35.3),
          #keep=c("score", "treatTRUE", "score_treat"),
          #coef_map=c("score"="Raw Score", 
                   # "treatTRUE"="Treatment",
                    #"score_treat"="Score x Treat"),
          #gof_map=c("nobs", "r.squared"),
          #add_rows=rows)



```

Question 7

The data is sensitive to the bandwidth.
```{r, echo = F}
data.rd3 <- data_raw %>%
  filter(Star_Rating==2.5 | Star_Rating==3)%>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window2 = (score>=-.1 & score<=.1),
         window3 = (score>=-.12 & score<=.12),
         window4 = (score>=-.13 & score<=.13),
         window5 = (score>=-.14 & score<=.14),
         window6 = (score>=-.15 & score<=.15),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star25.2 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd3 %>% filter(window2==TRUE)))
star25.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd3 %>% filter(window3==TRUE)))
star25.4 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd3 %>% filter(window4==TRUE)))
star25.5 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd3 %>% filter(window5==TRUE)))
star25.6 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd3 %>% filter(window6==TRUE)))

est2 <- as.numeric(star25.2$coef[3])
est3 <- as.numeric(star25.3$coef[3])
est4 <- as.numeric(star25.4$coef[3])
est5 <- as.numeric(star25.5$coef[3])
est5 <- as.numeric(star25.6$coef[3])

bandwidth <- c("0.1", "0.12", "0.13", "0.14", "0.15")
estimates <- c(est1, est2, est3, est4, est5)

three_stars <- data.frame(bandwidth,estimates)
three_stars


data.rd4 <- data_raw %>%
  filter(Star_Rating==3 | Star_Rating==3.5)%>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window2 = (score>=-.1 & score<=.1),
         window3 = (score>=-.12 & score<=.12),
         window4 = (score>=-.13 & score<=.13),
         window5 = (score>=-.14 & score<=.14),
         window6 = (score>=-.15 & score<=.15),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star35.2 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd4 %>% filter(window2==TRUE)))
star35.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd4 %>% filter(window3==TRUE)))
star35.4 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd4 %>% filter(window4==TRUE)))
star35.5 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd4 %>% filter(window5==TRUE)))
star35.6 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd4 %>% filter(window6==TRUE)))

est2 <- as.numeric(star35.2$coef[3])
est3 <- as.numeric(star35.3$coef[3])
est4 <- as.numeric(star35.4$coef[3])
est5 <- as.numeric(star35.5$coef[3])
est5 <- as.numeric(star35.6$coef[3])

bandwidth <- c("0.1", "0.12", "0.13", "0.14", "0.15")
estimates <- c(est1, est2, est3, est4, est5)

three_five_stars <- data.frame(bandwidth,estimates)
three_five_stars
```

Question 8

It looks like the data is clustered aaround the threshold.
```{r, echo = F}
ggplot(data.rd1, aes(x=score)) + 
  geom_bar(width=.025) + theme_bw() +
  labs(
    x="Running Variable",
    y="Number of Plans",
    title="Distribution of Raw Scores"
  ) 
```

Question 9

I don't know which variable is the HMOs and I can't get the love plot to work.

match.dat <- matchit(treat~partd, 
                     data=data.rd1 %>% 
                       filter(window2==TRUE, 
                              !is.na(treat), 
                              !is.na(premium_partc), 
                              !is.na(ma_rate)),
                     method=NULL, distance="mahalanobis")
love.plot(match.dat, abs=TRUE)     

```{r, echo = F}
data.rd1$partd
```

Question 10
I thik increasing star rating will cause enrollments to go up because people will be more confident in the quality.