---
title: "Homework Four Submission 2"
author: "Safia Read"
format:
  pdf:
    output-file: "read-s-hwk4-2"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

This is my second submission of the fourth homework for Econ 470. 

[Link to Github](https://github.com/safiaread/homework_4)

https://github.com/safiaread/homework_4

```{r, echo = F, message = F}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, fixest, xtable, modelsummary, rdrobust, MatchIt)
data <- read_rds("/Users/safiaread/Desktop/homework_4/data/output/final_ma_data.rds")
data <- data %>% 
subset(year >= 2010 & year <= 2015 & snp == "No" & !is.na(partc_score) & (planid < 800 | planid >= 900))

```

Question 1
It looks like the number of plans is pretty low.
```{r, echo = F, message = F}
q1<- data %>%
  group_by(fips, year) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = factor(year), y = count)) +
  geom_boxplot(outlier.shape = NA) +
  labs(title = "Boxplot of Counts by County", x = "County", y = "Count")+
  ylim(0,40)

#Have dropped outliers
```

Question 2
The star ratings have increased generally. 
```{r, echo = F, message = F}
data%>%
filter(year == 2010)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()

data%>%
filter(year == 2012)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()

data%>%
filter(year == 2015)%>%
ggplot(aes(x = Star_Rating)) +
geom_histogram()
```

Question 3

The average benchmark has fallen according to this graph, but I think the variable calculation is off.
```{r, echo = F}
q3 <- data%>%
group_by(year)%>%
summarise(avg_benchmark = mean(ma_rate, na.rm = T))
#he grouped by ssa but makes mine look insane

ggplot(q3, aes(x = year, y = avg_benchmark))+
geom_line()
```

Question 4

Medicare Advantage has increased in popularity over time. I would expect that to correlate with increased benchmark payments.
```{r, echo = F}
q4 <- data %>%
  group_by(year) %>%
  summarize(med_prop = sum(avg_enrollment, na.rm = TRUE) / sum(avg_eligibles, na.rm = TRUE))
  
ggplot(q4, aes(x = year, y = med_prop)) +
geom_line()

#This one has become f**ked up, fix this!

#Attempt 2 w/t first instead of mean
q4 <- data %>%
  group_by(year) %>%
  summarize(med_prop = first(avg_enrollment, na.rm = TRUE) / first(avg_eligibles, na.rm = TRUE), bench = mean(ma_rate, na.rm = TRUE))
```

Question 5
```{r, echo = F}
data_raw <- data %>%
  mutate(raw_rating=rowMeans(
    cbind(breastcancer_screen,rectalcancer_screen,cv_cholscreen,diabetes_cholscreen,
          glaucoma_test,monitoring,flu_vaccine,pn_vaccine,physical_health,
          mental_health,osteo_test,physical_monitor,primaryaccess,
          hospital_followup,depression_followup,nodelays,carequickly,
          overallrating_care,overallrating_plan,calltime,
          doctor_communicate,customer_service,osteo_manage,
          diabetes_eye,diabetes_kidney,diabetes_bloodsugar,
          diabetes_chol,antidepressant,bloodpressure,ra_manage,
          copd_test,betablocker,bladder,falling,appeals_timely,
          appeals_review),
    na.rm=T)) %>%
  select(contractid, planid, fips, avg_enrollment, state, county, raw_rating, partc_score,
         avg_eligibles, avg_enrolled, premium_partc, risk_ab, Star_Rating,
         bid, avg_ffscost, ma_rate, plan_type, partd)

q5 <-data_raw %>%
  select(raw_rating, Star_Rating) %>%
  mutate(three = sum(ifelse(raw_rating >= 2.75 & raw_rating < 3 & Star_Rating == 3, 1, 0), na.rm = TRUE), 
         three_five = sum(ifelse(raw_rating >= 3.25 & raw_rating < 3.5 & Star_Rating == 3.5, 1, 0), na.rm = TRUE), 
         four = sum(ifelse(raw_rating >= 3.75 & raw_rating < 4 & Star_Rating == 4, 1, 0), na.rm = TRUE), 
         four_five = sum(ifelse(raw_rating >= 4.25 & raw_rating < 4.5 & Star_Rating == 4.5, 1, 0), na.rm = TRUE), 
         five = sum(ifelse(raw_rating >= 4.75 & raw_rating < 5 & Star_Rating == 5, 1, 0), na.rm = TRUE))


#mutate error
q5[1,3:7]
```

Question 6
```{r, echo = F}
data.rd1 <- data_raw %>%
  filter(Star_Rating==2.5 | Star_Rating==3)%>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window1 = (score>=-.125 & score<=.125),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star25.1 <- lm(mkt_share ~ score + treat, data=data.rd1)
star25.2 <- lm(mkt_share ~ score + treat, data= (data.rd1 %>% filter(window1==TRUE)))
star25.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd1 %>% filter(window1==TRUE)))
est1 <- as.numeric(star25.1$coef[3])
est2 <- as.numeric(star25.2$coef[3])
est3 <- as.numeric(star25.3$coef[3])

bandwidth <- c("0.2", "0.125", "0.125")
estimates <- c(est1, est2, est3)

three_stars <- data.frame(bandwidth,estimates)
three_stars

ma.rd275 <- data_raw %>%
  filter(Star_Rating==2.5 | Star_Rating==3) %>%
  mutate(score = raw_rating - 2.75,
         treat = (score >= 0),
         window2 = (score >= -.125 & score <= .125),
         mkt_share = avg_enrollment / avg_eligibles,
         ln_share = log(mkt_share),
         score_treat = score * treat)


est275 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.125, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
              
summary(est275)

#rows <- tribble(~term, ~ m1, ~ m2, ~ m3 ,
              #  'Bandwidth', "0.25", "0.125", "0.#125")
#attr(rows, 'position')  <- 7

#modelsummary(list(star25.1, star25.2, star25.3),
         # keep=c("score", "treatTRUE", "score_treat"),
         # coef_map=c("score"="Raw Score", 
        #            "treatTRUE"="Treatment",
         #           "score_treat"="Score x Treat"),
        #  gof_map=c("nobs", "r.squared"),
        #  add_rows=rows)

data.rd2 <- data_raw %>%
  filter(Star_Rating==3 | Star_Rating==3.5) %>%
  mutate(score = raw_rating - 2.25,
         treat = (score>=0),
         window1 = (score>=-.125 & score<=.125),
         mkt_share = avg_enrollment/avg_eligibles,
         ln_share = log(mkt_share),
         score_treat=score*treat)
star35.1 <- lm(mkt_share ~ score + treat, data=data.rd2)
star35.2 <- lm(mkt_share ~ score + treat, data= (data.rd2 %>% filter(window1==TRUE)))
star35.3 <- lm(mkt_share ~ score + treat + score_treat, data= (data.rd2 %>% filter(window1==TRUE)))
est1 <- as.numeric(star35.1$coef[3])
est2 <- as.numeric(star35.2$coef[3])
est3 <- as.numeric(star35.3$coef[3])

bandwidth <- c("0.2", "0.125", "0.125")
estimates <- c(est1, est2, est3)

threefive_stars <- data.frame(bandwidth,estimates)
threefive_stars

#rows <- tribble(~term, ~ m1, ~ m2, ~ m3 ,
              #  'Bandwidth', "0.25", "0.125", "0.125")
#attr(rows, 'position')  <- 7

#modelsummary(list(star35.1, star35.2, star35.3),
          #keep=c("score", "treatTRUE", "score_treat"),
          #coef_map=c("score"="Raw Score", 
                   # "treatTRUE"="Treatment",
                    #"score_treat"="Score x Treat"),
          #gof_map=c("nobs", "r.squared"),
          #add_rows=rows)

ma.rd325 <- data_raw %>%
  filter(Star_Rating==3 | Star_Rating==3.5) %>%
  mutate(score = raw_rating - 3.25,
         treat = (score >= 0),
         window2 = (score >= -.125 & score <= .125),
         mkt_share = avg_enrollment / avg_eligibles,
         ln_share = log(mkt_share),
         score_treat = score * treat)


est325 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.125, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
              
summary(est325)

```

Question 7

The data is sensitive to the bandwidth and changes the estimate.
```{r, echo = F}

ma.rd275 <- data_raw %>%
  filter(Star_Rating==2.5 | Star_Rating==3) %>%
  mutate(score = raw_rating - 2.75,
         treat = (score >= 0),
         window2 = (score >= -.125 & score <= .125),
         mkt_share = avg_enrollment / avg_eligibles,
         ln_share = log(mkt_share),
         score_treat = score * treat)


est275_1 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.1, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
est275_2 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.12, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
est275_3 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.13, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")              
est275_4 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.14, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")         
est275_5 <- rdrobust(y=ma.rd275$mkt_share, x=ma.rd275$score, c=0,
                 h=0.15, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")     

summary(est275)

bandwidth <- c("0.1", "0.12", "0.13", "0.14", "0.15")
estimates <- c(est275_1$coef[1], est275_2$coef[1], est275_3$coef[1], est275_4$coef[1], est275_5$coef[1])

three_stars <- data.frame(bandwidth,estimates)
three_stars


est325_1 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.1, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
est325_2 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.12, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")
est325_3 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.13, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")              
est325_4 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.14, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")         
est325_5 <- rdrobust(y=ma.rd325$mkt_share, x=ma.rd325$score, c=0,
                 h=0.15, p=1, kernel="uniform", vce="hc0",
                 masspoints="off")     


bandwidth <- c("0.1", "0.12", "0.13", "0.14", "0.15")
estimates <- c(est325_1$coef[1], est325_2$coef[1], est325_3$coef[1], est325_4$coef[1], est325_5$coef[1])

threefive_stars <- data.frame(bandwidth,estimates)
threefive_stars

#rdrobust(y=ma.rd375$mkt_share, x=ma.rd375$score, c=0,
            #     h=0.125, p=1, kernel="uniform", vce="hc0",
           #      masspoints="off")
```

Question 8

It looks like the data is clustered aaround the threshold.
```{r, echo = F}
  ggplot(data_raw, aes(x=raw_rating)) + 
  geom_density() + theme_bw() +
  labs(
    x="Running Variable",
    y="Number of Plans",
    title="Distribution of Raw Scores for 2.75 Cutoff"
  ) +
  geom_vline(xintercept = 2.75, linetype = "dashed", color = "red")+
  scale_x_continuous(limits=c(2.5,3))
  #add scale limits

  ggplot(data_raw, aes(x=raw_rating)) + 
  geom_density() + theme_bw() +
  labs(
    x="Running Variable",
    y="Number of Plans",
    title="Distribution of Raw Scores for 3.25 Cutoff"
  ) +
  geom_vline(xintercept = 3.25, linetype = "dashed", color = "red")+
  scale_x_continuous(limits=c(3,3.5))
  
  #scale_x_continous()
  #add scale limits

```

Question 9

From my binned scatterplots, we can see some covariate imbalance around the proportion of HMO plans, with a higher proportion of HMO's being above the 3.5 threshold. For the Part D plans, there seems to be a lower proprtion of them past the 3.5 threshold. There isn't a lot of data around the 3 star threshold.

```{r, echo = F}

q9 <- data_raw %>%
  mutate(hmo = ifelse(plan_type == "HMO/HMOPOS", 1, 0), 
         dummy_partd = ifelse(partd == "Yes", 1, 0)) %>%
  group_by(raw_rating) %>%
  summarise(prop_hmo = mean(hmo), prop_d = mean(dummy_partd))

q9$dummy_partd

q9 %>%
  mutate(bin = ntile(prop_hmo, n = 30)) %>%
  group_by(bin) %>%
  summarise(xmean = mean(raw_rating), ymean = mean(prop_hmo)) %>%
  ggplot(aes(x = xmean, y = ymean)) + 
  geom_point() +
  geom_vline(xintercept = 2.75, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 3.25, linetype = "dashed", color = "blue") +
  scale_x_continuous(limits = c(2.5, 3.5))+
  labs(title = "HMOs")

q9 %>%
  mutate(bin = ntile(prop_d, n = 20)) %>%
  group_by(bin) %>%
  summarise(xmean = mean(raw_rating), ymean = mean(prop_d)) %>%
  ggplot(aes(x = xmean, y = ymean)) + 
  geom_point() +
  geom_vline(xintercept = 2.75, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 3.25, linetype = "dashed", color = "blue") +
  scale_x_continuous(limits = c(2.5, 3.5))+
  labs(title = "Part D")

#covariate balance from homework 2
```

Question 10

Increasing star rating caused enrollments to decrease slightly over estimates with small bandwidths. I'm not sure why, maybe my estimates are off.